### 2018-04-16 paper.Rmd
added a schema figure

>>>>

```{r database-schema, fig.pos="h", out.width = "95%", fig.cap="Database schema for childes-db. Tokens are linked to superordinate groupings of utterances, transcripts, corpora, and collections (red arrows). All tokens and utterances are additionally associated with a participant (blue arrows)."}

png::readPNG(here::here("images/schema.png")) %>% grid::grid.raster()
```
